Chapter 4: Binocular combination in the Autonomic Nervous System

### 2024-01-11 manuscript.Rmd
Added osf download commands

contrastsdB <- 20*log10(c(6,12,24,48,96))
colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
colpalmod <- c('#808080','#8B8000','#FE5000','#8783CF')
targetelectrodes <- c('Oz','POz','O1','O2')

@@

# (download and) analyse individual participant data for the luminance condition
if (processdata > 2){

  for(p in 601:612){
    participant <- paste0('P',p)

@@

    repcounterP <- (1:60)*0
    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(d)){
        tic()
        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))

@@

        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

@@

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,participant,'_summaryLum.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
  }

@@

# load in individual participant data and average, save group data
if (processdata > 1){

@@

@@

# generate plot showing the group pupillometry data for the luminance condition
if (processdata > 0){

@@

# (download and) analyse individual participant data for the melanopsin condition
if (processdata > 2){

  for(p in 501:512){
    participant <- paste0('P',p)

@@

    repcounterP <- (1:60)*0
    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(d)){
        tic()
        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))

@@

        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

@@

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,participant,'_summaryMel.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
    }
  }
```

@@

# load in individual participant data and average, save group data
if (processdata > 1){

@@

@@

# generate plot showing the group pupillometry data for the melanopsin experiment
if (processdata > 0){

@@

# (download and) analyse individual participant data for the L-M condition
if (processdata > 2){

  for(p in 701:712){
    participant <- paste0('P',p)

@@

    repcounterP <- (1:60)*0
    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(d)){
        tic()
        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))

@@

        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

@@

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,participant,'_summaryLM.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
  }

@@

# load in individual participant data and average, save group data
if (processdata > 1){

@@

@@

# generate plot showing the group pupillometry data for the L-M experiment
if (processdata > 0){

@@

  for(p in 301:312){
    participant <- paste0('P',p)

@@

    repcounterP <- (1:60)*0
    d <- dir(paste0(rawdir,participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(d)){
        tic()
        adata <- read.csv(paste0(rawdir,participant,'/',paste0(participant,'_S',block),'_annotations.csv'))

@@

        pdata <- read.csv(paste(rawdir,participant,'/',paste0(participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

@@

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,participant,'_summaryS.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))
  }

@@

# load in individual participant data and average, save group data
if (processdata > 1){

@@

@@

# generate plot showing the group pupillometry data for the S experiment
if (processdata > 0){

>>>>

contrastsdB <- 20*log10(c(6,12,24,48,96))
colpal <- c('#FE5000','#8783CF','#228B22','#808080','#6d008b','#8B8000')
colpalmod <- c('#808080','#8B8000','#FE5000','#8783CF')

@@

# (download and) analyse individual participant data for the luminance experiment
if (processdata > 2){

  for(participant in 1:24){

    # only download and process data if this has not been done already for this participant
    if (!file.exists(paste0(datadir,'P',600+participant,'summary.RData'))){

      # if there is no directory for this participant's data
      if (!file.exists(paste0(rawdir,'P',600+participant))){
        dir.create(paste0(rawdir,'P',600+participant))

       d <- dir(paste0(rawdir,'P',600+participant))

       if (length(d)==0){

         # if the tar file of this participant's data doesn't exist
         if (!file.exists(paste0(rawdir,'P',600+participant,'.zip'))){
           # download it from OSF
           if (!exists('osffiles')){
           osfnode <- '6u7db'
           osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffiles$name==paste0('P',600+participant,'.zip'))
          osf_download(osffiles[fid,],rawdir,progress=TRUE)
         }

         # then unzip the tar file
         unzip(paste0(rawdir,'P',600+participant,'.zip'),exdir=paste0(rawdir))

         # and delete the tar file to save storage space
         file.remove(paste0(rawdir,'P',600+participant,'.zip'))
       }
      }

      d <- dir(paste0(rawdir,'P',600+participant),full.names=TRUE)

@@

    repcounterP <- (1:60)*0
    afiles <- dir(path=paste0(rawdir,'P',600+participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(afiles)){
        tic()
        adata <- read.csv(paste0(rawdir,'P',600+participant,'/',paste0('P',600+participant,'_S',block),'_annotations.csv'))

@@

        pdata <- read.csv(paste(rawdir,'P',600+participant,'/',paste0('P',600+participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

@@

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,'P',600+participant,'_summaryLum.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))

    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
  }

  }}
```

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',600+participant,'summaryLum.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',600+participant,'summaryLum.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# generate plot showing the group pupillometry data for the luminance experiment

         if (!file.exists(paste0(datadir,'AveragedataLum.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name=='AveragedataLum.RData')
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }

@@

@@

# (download and) analyse individual participant data for the melanopsin experiment
if (processdata > 2){

  for(participant in 1:24){

    # only download and process data if this has not been done already for this participant
    if (!file.exists(paste0(datadir,'P',500+participant,'summary.RData'))){

      # if there is no directory for this participant's data
      if (!file.exists(paste0(rawdir,'P',500+participant))){
        dir.create(paste0(rawdir,'P',500+participant))

       d <- dir(paste0(rawdir,'P',500+participant))

       if (length(d)==0){

         # if the tar file of this participant's data doesn't exist
         if (!file.exists(paste0(rawdir,'P',500+participant,'.zip'))){
           # download it from OSF
           if (!exists('osffiles')){
           osfnode <- 'xkgd9'
           osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffiles$name==paste0('P',500+participant,'.zip'))
          osf_download(osffiles[fid,],rawdir,progress=TRUE)
         }

         # then unzip the tar file
         unzip(paste0(rawdir,'P',500+participant,'.zip'),exdir=paste0(rawdir))

         # and delete the tar file to save storage space
         file.remove(paste0(rawdir,'P',500+participant,'.zip'))
       }
      }

      d <- dir(paste0(rawdir,'P',500+participant),full.names=TRUE)

@@

    repcounterP <- (1:60)*0
    afiles <- dir(path=paste0(rawdir,'P',500+participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(afiles)){
        tic()
        adata <- read.csv(paste0(rawdir,'P',500+participant,'/',paste0('P',500+participant,'_S',block),'_annotations.csv'))

@@

        pdata <- read.csv(paste(rawdir,'P',500+participant,'/',paste0('P',500+participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

@@

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,'P',500+participant,'_summaryMel.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))

    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
    }
  }}
```

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',500+participant,'summaryMel.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',500+participant,'summaryMel.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# generate plot showing the group pupillometry data for the melanopsin experiment 
if (!file.exists(paste0(datadir,'AveragedataMel.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name=='AveragedataMel.RData')
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }

@@

@@

# (download and) analyse individual participant data for the L-M experiment
if (processdata > 2){

  for(participant in 1:24){

    # only download and process data if this has not been done already for this participant
    if (!file.exists(paste0(datadir,'P',700+participant,'summary.RData'))){

      # if there is no directory for this participant's data
      if (!file.exists(paste0(rawdir,'P',700+participant))){
        dir.create(paste0(rawdir,'P',700+participant))

       d <- dir(paste0(rawdir,'P',700+participant))

       if (length(d)==0){

         # if the tar file of this participant's data doesn't exist
         if (!file.exists(paste0(rawdir,'P',700+participant,'.zip'))){
           # download it from OSF
           if (!exists('osffiles')){
           osfnode <- 'pexyk'
           osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffiles$name==paste0('P',700+participant,'.zip'))
          osf_download(osffiles[fid,],rawdir,progress=TRUE)
         }

         # then unzip the tar file
         unzip(paste0(rawdir,'P',700+participant,'.zip'),exdir=paste0(rawdir))

         # and delete the tar file to save storage space
         file.remove(paste0(rawdir,'P',700+participant,'.zip'))
       }
      }

      d <- dir(paste0(rawdir,'P',700+participant),full.names=TRUE)

@@

    repcounterP <- (1:60)*0
    afiles <- dir(path=paste0(rawdir,'P',700+participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(afiles)){
        tic()
        adata <- read.csv(paste0(rawdir,'P',700+participant,'/',paste0('P',700+participant,'_S',block),'_annotations.csv'))

@@

        pdata <- read.csv(paste(rawdir,'P',700+participant,'/',paste0('P',700+participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

@@

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,'P',700+participant,'_summaryLM.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))

    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
  }

  }}
```

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',700+participant,'summaryLM.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',700+participant,'summaryLM.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# generate plot showing the group pupillometry data for the L-M experiment
if (!file.exists(paste0(datadir,'AveragedataLM.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name=='AveragedataLM.RData')
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }

@@

@@

  for(participant in 1:24){

    # only download and process data if this has not been done already for this participant
    if (!file.exists(paste0(datadir,'P',300+participant,'summary.RData'))){

      # if there is no directory for this participant's data
      if (!file.exists(paste0(rawdir,'P',300+participant))){
        dir.create(paste0(rawdir,'P',300+participant))

       d <- dir(paste0(rawdir,'P',300+participant))

       if (length(d)==0){

         # if the tar file of this participant's data doesn't exist
         if (!file.exists(paste0(rawdir,'P',300+participant,'.zip'))){
           # download it from OSF
           if (!exists('osffiles')){
           osfnode <- 'k9mdq'
           osfproject <- osf_retrieve_node(osfnode)
          osffiles <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffiles$name==paste0('P',300+participant,'.zip'))
          osf_download(osffiles[fid,],rawdir,progress=TRUE)
         }

         # then unzip the tar file
         unzip(paste0(rawdir,'P',300+participant,'.zip'),exdir=paste0(rawdir))

         # and delete the tar file to save storage space
         file.remove(paste0(rawdir,'P',300+participant,'.zip'))
       }
      }

      d <- dir(paste0(rawdir,'P',300+participant),full.names=TRUE)

@@

    repcounterP <- (1:60)*0
    afiles <- dir(path=paste0(rawdir,'P',300+participant),pattern='*annotations.csv',full.names=TRUE)

    for (block in 1:length(afiles)){
        tic()
        adata <- read.csv(paste0(rawdir,'P',300+participant,'/',paste0('P',300+participant,'_S',block),'_annotations.csv'))

@@

        pdata <- read.csv(paste(rawdir,'P',300+participant,'/',paste0('P',300+participant,'_S',block),'_pupil_positions.csv',sep=''))
        pdata2 <- pdata[,c(1,3,4,14)]
        pdata2 <- pdata2[which(pdata2[,3]>0.2),]

@@

    meanwavesP <- apply(pupilwaveforms[,,c(15,20),],4,mean,na.rm=TRUE)
    meanspectraP <- apply(pupilspectra[,,c(15,20),],4,mean,na.rm=TRUE)
    save(file=paste(datadir,'P',300+participant,'_summaryS.RData',sep=''),list=c('cleanmeansP','cleanmasksP','cleanmeansP2','cleanmasksP2','meanspectraP','meanwavesP'))

    if (cleanupraw==1){file.remove(d)} # delete raw data files to save space
  }

  }}
```

@@

# load in individual participant data and average, save group data
if (processdata > 1){
  for (participant in 1:24){
         # if the summary file of this participant's data doesn't exist
         if (!file.exists(paste0(datadir,'P',300+participant,'summaryS.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name==paste0('P',300+participant,'summaryS.RData'))
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }
}

@@

# generate plot showing the group pupillometry data for the S experiment
if (!file.exists(paste0(datadir,'AveragedataS.RData'))){
           # download it from OSF
           if (!exists('osffilesP')){
           osfnode <- '9ebtd'
           osfproject <- osf_retrieve_node(osfnode)
          osffilesP <- osf_ls_files(osfproject,n_max=300)}
          fid <- which(osffilesP$name=='AveragedataS.RData')
          osf_download(osffilesP[fid,],datadir,progress=TRUE)
         }

@@
